\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Exam 3 Written}
\author{Benny Chen}
\date{\today}

\usepackage{color}
\usepackage{amsthm}
\usepackage{amssymb} 
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\begin{document}

\maketitle

\section*{Problem 1}

Alan recently came across the concept of ensemble methods in a data mining class and decided to apply it to stock market prediction. In order to predict whether the stock market will rise or fall on a given day, he decided to flip a coin 1000 times and predicted the stock market to go up if heads turn up in majority and vice-versa. He thinks that this approach could get him a better prediction of the stock market because an ensemble of independent classifiers could potentially obtain a better prediction. Do you agree with him?
Give a brief justification.

I disagree with Alan as a coin flip to predict the stock market is not a reliable method for predicting financial markets. Coin flips are independent events and do not have any correlation to the stock market. Coin flips are a random binary process of being heads or tails. Ensemble methods would help as it uses multiple algorithms to output and combinine their outputs to produce a more accurate overall prediction. For a ensemble method to have better predictions there needs to be diversity and quality of the individual classifiers used. Overall I think ensemble methods can be great for predicting stock markets but for this purpose simply flipping a coin would not work.

\section*{Problem 2}

Consider running a single iteration of AdaBoost on three sample points, starting with uniform weights on the sample points. All the ground truth labels and predictions are either $+1$ or $-1$. In the table below, some values have been omitted.

\begin{table}[h]
    \begin{tabular}{lllll}
    \hline
          & True Label & Classifier Prediction & Initial Weight & Updated Weight \\ \hline
    $X_1$ & -1         & -1                    & 1/3            & ?              \\
    $X_2$ & ?          & +1                    & 1/3            & $\sqrt2/3$    \\
    $X_3$ & ?          & ?                     & 1/3            & $\sqrt2/6$    \\ \hline
    \end{tabular}
    \centering
\end{table}

Is $X_2$ misclassified? Is $X_3$ misclassified?

Yes both $X_2$ and $X_3$ are misclassified. 

\end{document}